---
title: "Generate signatures"
author: "Tiago Maié"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to update a released site}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---



```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## CimpleG (Simple CpG signatures)

* CimpleG tries to find the CpGs that best classify a cell-type given a train dataset
* It also enables you to perform cell-type deconvolution in a couple of easy steps
* It can use beta or M values
* Here we show how easy it is to generate a signatures

### Installation

If you haven't installed CimpleG, you can find the instructions to do so [here](https://costalab.github.io/CimpleG/#installation).
However it should be as simple as:

```{r install_cimpleg, eval=FALSE}
if(!require("CimpleG")) devtools::install_github("costalab/CimpleG")
```

### Loading package

We load the CimpleG package.

```{r load_cimpleg}
library("CimpleG")
```

### Loading data

In this tutorial, we will use a small dataset with just 409 samples and 1000 CpGs.
We will also use a table with metadata regarding these samples.
This dataset comes included with CimpleG. You can read more about it [here]().

```{r load_data}
# load data
data(train_data)
data(train_targets)
```

### Running CimpleG

Running CimpleG can be quite simple. You just need to run the CimpleG function with a few parameters.

```{r cimpleg}
# run CimpleG
cimpleg_result <- CimpleG(
  train_data,
  train_targets,
  target_columns = c("CELL_TYPE_BLOOD.CELLS","CELL_TYPE_HEPATOCYTES"),
  train_only = TRUE,
  method = "CimpleG"
)
```

Here we are generating signatures to find leukocytes and hepatocytes.

We can quickly visualize how our signature is able to separate the data.

```{r plot_cimpleg}
# plot_signature(cimpleg_result,train_data)
# TODO
```



